\chapter{Sources / References} 
\section{Bremaud, Mathematical Principles of Sig-
nal Processing : Fourier and Wavelet Anal-
ysis}
\label{sec:Bremaud, Mathematical Principles of Sig-
nal Processing : Fourier and Wavelet Anal-
ysis}
\begin{itemize}
  \item Introduction to Fourier Analysis in L 1
  \item appendix on Lebesgue integral
  \item Signal Processing impulse response, frequency response, band-pass Sig-
nals, sections on sampling, DSP, Subband Coding.
  \item Fourier analysis in L 2
  \item Wavelet Analysis with section on Windowed Fourier transform cover-
ing the uncertainty principle with WFT and Gabor’s inversion formula.
Wavelet transform, orthonormal expansions, construction of an MRA and
smooth MRA.
\end{itemize}

\section{Boggess and Narcowich, A First Course in
Wavelets with Fourier Analysis}
\label{sec:Boggess and Narcowich, A First Course in
Wavelets with Fourier Analysis}
\begin{itemize}
  \item Exercises with solutions!!!
  \item Inner product spaces : L 1 , L 2 , orthogonality, triangle inequalities, linear
operators , Least squares and predicitve coding.
  \item Fourier Series : Intro, computation convergence theorems
  \item Fourier Transform : informal development, properties and convolution,
linear filters, sampling theorem, uncertainty principle.
  \item discrete fourier analysis : discrete fourier transform, discrete signals
  \item Haar wavelet Analysis : why, Haar wavelets and properties, Decomposition
and Reconstruction Algorithms.
  \item MRA framework and what not. Decomposition and Reconstruction and
Wavelet spaces. 
\end{itemize}

\section{Kaiser, A Friendly Guide to Wavelets}
\begin{itemize}
    \item Background and notation for Dual Bases, innder product spaces, recipro-
cal bases, function spaces, fourier Series, integrals signal processing.
    \item Windowed FT : motivation and definition. time-frequency localization.
The reconstruction formula. Singals processing in time-frequency domain.
    \item Continuous wavelet transforms
    \item Generalized Frames
    \item Discrete time-frequency : Analysis and Sampling
    \item Discrete time-scake analysis
    \item MRA
    \item other stuff (physics)
\end{itemize}

\section{Sidney Burrus and Guo, Introduction to Wavelets and Wavelet Transforms}
\label{sec:Sidney Burrus and Guo, Introduction to Wavelets and Wavelet Transforms}
Covers only wavelets. Goes quite quickly into MRA (p. 10) Should be used just
for MRA I think.

\section{Mallat, A Wavelet Tour of Signal Processing}
\label{sec:Mallat, A Wavelet Tour of Signal Processing}
This one is a monster (630 pages) this will definitely be referenced often. Shouldn’t
be used until after fourier series are finished. Good for Fourier transform and
time-frequency properties.
\begin{itemize}  
  \item Introduction to time-frequency (Time-Frequency Atoms, Bases)
  \item Fourier Kingdom(Impulse response, transfer function, L 1 , L 2 , Properties
and uncertainty principle.
 \item Discrete Revolution and finite signals.
 \item Time meets frequency (Time-Frequency Atoms, Windowed Fourier Trans-
form, Wavelet Transforms)
 \item Frames
 \item Wavelet Zoom
 \item Wavelet Bases (orthogonal filter banks, classes)
\end{itemize}

\section{Stein and Shakarchi, Fourier Analysis : An Introduction}
\label{sec:Stein and Shakarchi, Fourier Analysis : An Introduction}
\section{James, A Student’s Guide to Fourier Trans-
forms }
\section{Gasquet and Witomski, Analyse De Fourier
et Applications : Filtrage, calcul numérique
et ondelettes}
























